Hierarchical Controller Architecture for SDN

### 2013-11-05 presentation/ppt.tex
Update again

\frame{
\frametitle{Simulation}
\begin{itemize}
	\item Wrote a simulator to simulate a hierarchical controller architecture\footnote{code @ https://github.com/MugiwaraLuffy/ACN/tree/master/simulator/src/graph}
	\item A minimal API for control plane, data plane, controller behavior, etc have been defined
	\item A $Node$ is an element in the network which implements a control plane interface 
	\item A $Switch$ extends a $Node$ and contains a data plane
	\item A $Controller$ extends a $Node$ and implements standard controller API
	\item $DataNetwork$ contains all the switches which handle actual data packets
	\item $ControlNetwork$ contains hierarchical layers of controllers
\end{itemize}
}

>>>>

\frame{
\frametitle{Simulation}
\begin{itemize}
	\item Wrote a simulator to simulate a hierarchical controller architecture\footnote{code @ https://github.com/MugiwaraLuffy/ACN/tree/master/simulator/src/swiconsim}
	\item A minimal set of APIs for control plane, data plane, controller behavior, etc has been defined
	\item A $Node$ is an element in the management network which implements $IControlPlane$ interface 
	\item A $Switch$ extends a $Node$ and contains a data plane
	\item A $Controller$ extends a $Node$ and implements standard controller APIs
	\item $DataNetwork$ contains all the switches which handle actual data packets
	\item A $Controller$ controls a $Node$ which could be a $Switch$ or another $Controller$
\end{itemize}
}
